A systematic search for transiting planets in the \KT\ data

### 2015-02-16 ms.tex
fixing a reference
some fpp text

A major problem with any transit search is the potential confusion between
transiting planets and eclipsing binaries.
Ground-based surveys prior to \kepler\ often had a false-positive rate
of 30 to 40~percent. \dfmtodo{(because of shit?) Because of giant pixels.
See references in Morton and Johnson intro, probably}
In the primary \kepler\ Mission, this number was significantly lower:
the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of the \kepler\ spacecraft.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
variations between transits \dfmtodo{(e.g. citation)}.

>>>>

A major problem with any transit search is the potential confusion
between transiting planets and stellar eclipsing binaries.  Of
particular concern are grazing stellar eclipses or stellar eclipses
that contribute only a small fraction of the total light in a target
star's photometric aperture, thus display greatly diluted eclipse
depths able to mimic the signals of small planets.

Ground-based transit surveys have experienced false-positive rates
well over 50\%.  For example, \citet{Latham:2009} reported eight
eclipsing binaries and one transiting planet among the sample of
transit candidates in one field of the Hungarian Automated Telescope
Network transit search.  In fact, the follow-up process to try to rule
out such astrophysical false positives is a large portion of the
effort that goes into a transit survey
\citep[e.g.,][]{Odonovan:2006,Almenara:2009,Poleski:2010}.

Despite this large fraction of astrophysical false positives in
ground-based surveys, the primary \kepler\ Mission saw a much lower
false positive rate \citep{Morton:2011, Fressin:2013}, primarily due
to two major factors.  First, the superior precision of
the \kepler\ photometry enabled

Ground-based surveys prior to \kepler\ often had a false-positive rate
of 30 to 40~percent. \dfmtodo{(because of shit?) Because of giant pixels.
See references in Morton and Johnson intro, probably}
In the primary \kepler\ Mission, this number was significantly lower:
the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of the \kepler\ spacecraft.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
variations between transits \dfmtodo{(e.g. citation)}.
